Interactive Curvature Tensor Visualization on Digital Surfaces\thanks{This work has been mainly funded by XXXXXXX research grants.}

### 2015-10-22 latex/article.tex
CCL

>>>>

In this article, we have propose a full data parallel framework on GPU
hardware which combines an adaptive isosurface construction from
digital data with a curvature tensor estimation at each vertex. Using
this approach, we can explore in realtime different curvature
measurements (mean, Gaussian, principal directions) with different
ball radii on potentially large dynamic dataset. Our proposal relies
on both a linear octree representation with Morton codes and an
efficient integral computation on GPU.  The source code and additional
material (video\ldots) are available on the project website
(\url{https://github.com/dcoeurjo/ICVT}).
